Time Series Bootstrapping For Solar Current

### 2021-12-16 deliverables/paper.Rmd
Minor fix

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost/kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. Stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour" (@energysage). In our calculations we used an hour window between 
8am to 4pm, a typical day range where the sun is overhead. A disclaimer,
some of the values at the beginning and end of the day may not hold 
exactly greater than our cutoff stated by Solar Reviews, however this range 
yielded the greatest results of solar irradiance and Wh, some being much larger
than 1000 W/m^2 and others being just under. Therefore, we are deciding to use 
this range as our peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of /$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning /$`r round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW)` yearly on one solar panel grid. 
Knowing this, any resident located in or around the Los Angeles area should
feel confident in their decision of purchasing a solar panel grid.

>>>>

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost/kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. Stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour" (@energysage). In our calculations we used an hour window between 
8am to 4pm, a typical day range where the sun is overhead. A disclaimer,
some of the values at the beginning and end of the day may not hold 
exactly greater than our cutoff stated by Solar Reviews, however this range 
yielded the greatest results of solar irradiance and Wh, some being much larger
than 1000 W/m^2 and others being just under. Therefore, we are deciding to use 
this range as our peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of \$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning \$`r round(round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW),2)` yearly on one solar panel grid. 
Knowing this, any resident located in or around the Los Angeles area should
feel confident in their decision of purchasing a solar panel grid.
